mixchar

### 2018-08-01 README.Rmd
fix build issue! move manuscript and logo folder to buildignore

---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

>>>>

---
title: "mixchar"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r top_banner, echo=FALSE, fig.height=3, fig.width=4}
knitr::include_graphics('logo/mixchar_logo.png')
```
